Quantum Walks and Application to Quantum Money

### 2025-01-25 main.tex
new commit

\section*{Introduction}
Quantum computation represents a paradigm shift in the way we process information. Rooted in quantum mechanics, it leverages principles such as \textit{superposition}, \textit{entanglement}, and \textit{quantum interference} to solve certain classes of problems exponentially faster than classical computers. As a field, it combines the rigor of mathematics, the elegance of physics, and the practicality of computer science to unlock new computational horizons.

@@

\subsection*{Qubits: The Building Blocks}
A \textit{qubit} (quantum bit) is the quantum analog of the classical bit. While a classical bit can hold a value of either 0 or 1, a qubit exists in a quantum state described as a combination of these two possibilities, written as:
\[
|\psi\rangle = \alpha|0\rangle + \beta|1\rangle
\]
Here:
\begin{itemize}
    \item $\alpha$ and $\beta$ are complex numbers that represent the probabilities of measuring the qubit in the 0 or 1 state, respectively.
    \item The condition $|\alpha|^2 + |\beta|^2 = 1$ ensures the total probability is conserved.
\end{itemize}
This \textit{superposition} property allows quantum computers to represent and process a vast amount of information simultaneously.

\subsection*{Entanglement: Quantum Correlations}
\textit{Entanglement} is a uniquely quantum phenomenon where the state of one qubit becomes intrinsically linked to the state of another, regardless of the physical distance between them. For example, two qubits might be in the entangled state:
\[
|\psi\rangle = \frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)
\]
If one qubit is measured, the state of the other is instantaneously determined. This property underpins many quantum technologies, including quantum teleportation and quantum cryptography.

@@

\section*{Quantum Algorithms}
Quantum algorithms exploit the principles of quantum mechanics to outperform classical counterparts in specific scenarios. Some groundbreaking algorithms include:

\subsection*{Shor's Algorithm}
Shor's algorithm efficiently factors large integers, threatening the security of classical cryptographic systems like RSA. Its speedup stems from the quantum Fourier transform and modular arithmetic in the quantum domain.

\subsection*{Grover's Algorithm}
Grover's algorithm provides a quadratic speedup for unstructured search problems. For instance, finding a specific item in an unsorted database with $N$ entries takes $O(\sqrt{N})$ queries on a quantum computer compared to $O(N)$ on a classical one.

\subsection*{Quantum Simulation}
Simulating quantum systems is computationally intensive for classical computers. Quantum computers can model chemical reactions, molecular structures, and physical systems more efficiently, accelerating drug discovery and materials science.

\subsection*{Quantum Approximation Optimization Algorithm (QAOA)}
Used for solving combinatorial optimization problems, QAOA is particularly relevant in fields like logistics and finance.

\section*{Applications and Impact}
Quantum computation has transformative potential across industries:
\begin{itemize}
    \item \textbf{Cryptography}: Beyond breaking classical systems, quantum computers can also enable secure communication through quantum key distribution (e.g., using entangled photons).
    \item \textbf{Machine Learning}: Quantum-enhanced machine learning algorithms can handle high-dimensional data spaces more efficiently.
    \item \textbf{Supply Chain and Logistics}: Quantum algorithms can optimize complex systems like traffic flow or supply chain logistics.
    \item \textbf{Physics and Chemistry}: Accurate simulation of atomic interactions can drive innovations in energy, materials, and pharmaceuticals.
\end{itemize}

\section*{Challenges in Quantum Computation}
\begin{itemize}
    \item \textbf{Quantum Decoherence}: Quantum states are fragile and can be disrupted by interactions with their environment. Building stable quantum systems requires sophisticated error correction techniques and noise mitigation strategies.
    \item \textbf{Error Correction}: Quantum error correction introduces redundancy through logical qubits composed of many physical qubits. This increases resource requirements significantly.
    \item \textbf{Scalability}: Scaling quantum computers to hundreds or thousands of qubits is a formidable engineering challenge. Current systems, like IBM's quantum processors and Google's Sycamore, are still in the \textit{noisy intermediate-scale quantum} (NISQ) era.
    \item \textbf{Algorithm Development}: Quantum algorithms for real-world problems are still under active research. Identifying practical applications with significant quantum advantage is a key focus.
\end{itemize}

\section*{Current Progress and the Future of Quantum Computation}
The quantum computing landscape is advancing rapidly:
\begin{itemize}
    \item \textbf{Hardware}: Companies like IBM, Google, Rigetti, IonQ, and D-Wave are pushing the boundaries of quantum hardware.
    \item \textbf{Software}: Frameworks like Qiskit, Cirq, and TensorFlow Quantum make quantum programming more accessible.
    \item \textbf{Commercial Applications}: Financial modeling, risk analysis, and supply chain optimization are emerging areas of interest for quantum technologies.
\end{itemize}
The \textit{quantum advantage}---where quantum computers outperform classical systems in practical tasks---has been demonstrated in specific scenarios (e.g., Google's quantum supremacy experiment in 2019). However, achieving broad-scale quantum advantage remains a long-term goal.

\section*{Conclusion}
Quantum computation stands at the forefront of a technological revolution. By rethinking computation through the lens of quantum mechanics, it opens new pathways for solving problems that were once thought intractable. Although challenges remain, the potential benefits are vast, with the promise of transforming industries and deepening our understanding of the universe. As research and development continue, quantum computation is set to redefine the future of technology and science.

\section{Introduction to Quantum Walks}

\section{Group Actions}

@@

>>>>

\section*{Introduction}

Quantum computing is a revolutionary field that combines quantum mechanics and information theory to redefine computation and information processing. In the latter part of the 20th century, scientists explored the fusion of quantum mechanics and information theory, leading to the birth of quantum information science. This field challenges the classical view of computation by introducing novel concepts like quantum bits (qubits), entanglement, and quantum superposition, which have enabled new algorithms and protocols that outpace their classical counterparts in specific tasks. Classical computers are grounded in bits, which take binary values (0 or 1). Quantum computing introduces the qubit, a fundamental unit of quantum information that can exist in a superposition of states, such as 0 and 1 simultaneously. This foundational difference enables quantum computers to process information in fundamentally new ways. Unlike technologies like DNA computing or optical computing, which describe changes in the physical substrate while retaining classical computational principles, quantum computing changes the computational paradigm itself. A quantum computer uses the principles of quantum mechanics, such as superposition and entanglement, rather than classical mechanics, to process information. In the 1980s, pioneers like Richard Feynman and David Deutsch recognized that certain quantum phenomena could not be efficiently simulated on classical computers. These insights led to the exploration of quantum Turing machines and quantum circuit models, which provided a theoretical framework for quantum computing. The discovery of quantum gates and their role in quantum algorithms formalized the field.

Early quantum algorithms demonstrated that quantum computing could solve certain problems more efficiently than classical methods. Notably, in 1994, Peter Shor introduced a polynomial-time quantum algorithm for integer factorization, which threatened classical cryptographic protocols relying on the difficulty of factoring large integers. Entanglement, a uniquely quantum phenomenon, allows particles to exhibit correlations that defy classical explanation. This property is crucial for many quantum algorithms and protocols, as it enables quantum computers to process and store information in a way that classical computers cannot. Two notable algorithms underscore the potential of quantum computing: Shor’s Algorithm, which efficiently factors integers, undermining RSA encryption and other cryptographic systems based on the hardness of factoring, and Grover’s Algorithm, which provides a quadratic speedup for unstructured search problems, such as searching an unsorted database. These algorithms exemplify the theoretical advantages of quantum computing over classical approaches, even though practical implementations remain challenging.

Quantum systems are fragile and susceptible to decoherence, where quantum states lose their coherence due to interactions with the environment. This makes maintaining quantum states for computation a significant challenge. Quantum error correction methods were developed to address decoherence and other quantum noise. The breakthrough work of Shor and Steane in the mid-1990s introduced error-correction codes that allowed reliable computation despite quantum noise. Building scalable quantum computers requires advances in hardware and experimental techniques. As of now, only small-scale quantum systems with a few qubits have been implemented successfully in laboratories. Quantum computing does not offer universal speedups for all problems. For example, Grover’s algorithm provides only a quadratic speedup for unstructured search, and certain problems remain equally challenging for both quantum and classical computers.

Quantum key distribution protocols, like BB84 and Ekert’s protocol, offer provably secure methods for communication based on the principles of quantum mechanics. Unlike classical cryptography, which relies on computational assumptions, quantum cryptography guarantees security through physical principles. The quantum perspective has provided new insights into classical computing and inspired novel classical algorithms. It has also advanced simulation techniques for quantum systems, benefiting fields like material science and chemistry. Quantum information processing has deepened our understanding of quantum mechanics, shedding light on foundational questions about quantum measurement and entanglement. For example, experiments testing Bell’s inequalities have confirmed the non-classical correlations predicted by quantum theory.

While practical quantum computing is still in its infancy, significant progress has been made. Quantum hardware companies like IBM, Google, and Rigetti have developed small-scale quantum processors capable of performing limited computations. Platforms such as Qiskit and Cirq enable researchers to experiment with quantum programming and algorithm development. Efforts to build scalable, fault-tolerant quantum computers are ongoing, alongside investigations into alternative models of quantum computation, such as topological and cluster-state quantum computing. Despite these advances, many open questions remain about the scope and ultimate power of quantum computation. While quantum computers will not replace classical ones for all tasks, they promise to revolutionize fields where their unique capabilities provide exponential speedups or new forms of computation.

Quantum computing represents a profound shift in how we understand and leverage computation. By replacing classical mechanics with quantum mechanics as the foundation for processing information, quantum computing has opened new avenues for scientific discovery and technological innovation. While challenges persist, the theoretical and experimental advances made thus far underscore the transformative potential of this exciting field.

@@

\section*{Understanding a Qubit}
A qubit (quantum bit) is the fundamental unit of quantum information, analogous to a classical bit. However, unlike a classical bit, which can only exist in one of two definite states ($0$ or $1$), a qubit can exist in a linear combination, or superposition, of both states simultaneously. Mathematically, the state of a single qubit is represented as:

\begin{equation}
|\psi\rangle = \alpha |0\rangle + \beta |1\rangle
\end{equation}

Here:
\begin{itemize}
    \item $|0\rangle$ and $|1\rangle$ are the basis states (analogous to $0$ and $1$ in classical computing).
    \item $\alpha$ and $\beta$ are complex numbers known as probability amplitudes.
\end{itemize}

The normalization condition \(|\alpha|^2 + |\beta|^2 = 1\) ensures that the probabilities of measuring the qubit in either the $|0\rangle$ or $|1\rangle$ state sum to 1.

The qubit's unique ability to exist in a superposition of states is what gives quantum computers their immense computational potential, enabling them to process and store information in fundamentally different ways than classical computers.

\section*{Superposition}
Superposition is a quantum phenomenon where a qubit exists in a combination of multiple states simultaneously. For example, a qubit in the state:

\begin{equation}
|\psi\rangle = \frac{1}{\sqrt{2}}|0\rangle + \frac{1}{\sqrt{2}}|1\rangle
\end{equation}

is in an equal superposition of $|0\rangle$ and $|1\rangle$. This means that if we measure the qubit, there is an equal probability (50\%) of observing it in either state.

Key properties of superposition:
\begin{itemize}
    \item \textbf{Parallelism:} When a quantum system is in superposition, it can perform computations for all possible states simultaneously. For instance, a single qubit can encode two states ($|0\rangle$ and $|1\rangle$) at the same time, while $n$ qubits can encode $2^n$ states.
    \item \textbf{Measurement Collapse:} When a qubit in superposition is measured, it collapses into one of its basis states, $|0\rangle$ or $|1\rangle$, with a probability given by $|\alpha|^2$ and $|\beta|^2$, respectively.
\end{itemize}

Superposition allows quantum systems to explore multiple possibilities in parallel, which is critical for quantum algorithms such as Grover's search or Shor's factoring.

\section*{Entanglement}
Entanglement is a uniquely quantum phenomenon where two or more qubits become correlated in such a way that the state of one qubit is directly related to the state of the other, regardless of the physical distance between them. When qubits are entangled, the measurement of one qubit instantly determines the state of the other.

An example of an entangled state for two qubits is the Bell state:

\begin{equation}
|\psi\rangle = \frac{1}{\sqrt{2}} (|00\rangle + |11\rangle)
\end{equation}

Here:
\begin{itemize}
    \item $|00\rangle$ means both qubits are in the $|0\rangle$ state.
    \item $|11\rangle$ means both qubits are in the $|1\rangle$ state.
\end{itemize}

If one qubit is measured to be $|0\rangle$, the other qubit will instantly collapse to $|0\rangle$, and similarly for $|1\rangle$, regardless of the distance between them.

Key features of entanglement:
\begin{itemize}
    \item \textbf{Non-Local Correlations:} Entanglement defies classical intuition, as it suggests that measurement outcomes are correlated even across vast distances, a phenomenon supported by experiments validating Bell's Theorem.
    \item \textbf{Applications:} Entanglement is a resource for many quantum technologies, including quantum teleportation, quantum cryptography (e.g., secure communication via the BB84 protocol), and quantum error correction.
\end{itemize}

Entanglement, along with superposition, forms the backbone of quantum computing and quantum communication, enabling capabilities that are impossible in the classical world.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction to Quantum Walks}

The concept of a \textit{quantum walk} is a quantum analog of the classical random walk and plays a significant role in quantum algorithms. There are two main types of quantum walks: \textit{continuous-time} and \textit{discrete-time} quantum walks, both of which exhibit behaviors that are significantly different from classical random walks.

\section*{Continuous-Time Quantum Walks}
A \textit{continuous-time quantum walk} is defined on a graph, where the evolution of the system is governed by a differential equation similar to the Schrödinger equation:
\[
i\frac{d}{dt}q(t) = Hq(t),
\]
where the Hamiltonian \( H \) is an \( N \times N \) Hermitian matrix, with \( H_{jk} = 0 \) if and only if vertices \( j \) and \( k \) are not connected. The vector \( q(t) \in \mathbb{C}^N \) contains the complex amplitudes corresponding to each vertex. Notably, the state space for the quantum walk is the same as that for the corresponding classical random walk.

One important matrix associated with the graph \( G \) is the \textit{Laplacian matrix}, defined as:
\[
L_{jk} =
\begin{cases}
-\text{deg}(j) & \text{if } j = k, \\
1 & \text{if } (j, k) \in E, \\
0 & \text{otherwise}.
\end{cases}
\]

The continuous-time random walk on \( G \) is then defined as the solution to the differential equation:
\[
\frac{d}{dt} p_j(t) = \sum_{k \in V} L_{jk} p_k(t),
\]
where \( p_j(t) \) represents the probability at vertex \( j \) at time \( t \). The solution to this equation can be expressed in closed form as:
\[
p(t) = e^{Lt} p(0),
\]
where \( L \) is the Laplacian matrix and \( p(0) \) is the initial condition.

This equation closely resembles the Schrödinger equation, but it lacks the factor \( i \). By adding this factor and redefining the probabilities \( p_j(t) \) as quantum amplitudes \( q_j(t) = \langle j|\psi(t)\rangle \) (where \( \{ |j\rangle : j \in V \} \) is an orthonormal basis for the Hilbert space), we obtain:
\[
i \frac{d}{dt} q_j(t) = \sum_{k \in V} L_{jk} q_k(t),
\]
which is the Schrödinger equation with the Laplacian of the graph as the Hamiltonian. Since the Laplacian is a Hermitian operator, these dynamics preserve normalization:
\[
\frac{d}{dt} \sum_{j \in V} |q_j(t)|^2 = 0.
\]

The solution to this differential equation is:
\[
|\psi(t)\rangle = e^{-iLt} |\psi(0)\rangle.
\]

A continuous-time quantum walk can also be defined using any Hermitian Hamiltonian that respects the structure of \( G \).

\subsection*{Differences from Classical Random Walks}
The evolution of a quantum walk, governed by a Hamiltonian, dictates state transitions over time while preserving normalization. This contrasts with classical random walks, which involve probabilistic transitions. Moreover, the wave nature of quantum mechanics introduces interference effects, enabling faster exploration of graphs compared to classical methods. For instance, on one-dimensional graphs, a classical random walk progresses at a rate proportional to the square root of time, while a quantum walk progresses linearly with time due to the wave-like propagation of quantum states.

\section*{Discrete-Time Quantum Walks}
\textit{Discrete-time quantum walks}, though more complex to define, provide a convenient framework for certain quantum algorithms, particularly quantum search algorithms.

In the simplest classical discrete-time random walk on a graph \( G \), at each time step, the walker moves from a given vertex to one of its neighbors with equal probability. This process is described by a \( |V| \times |V| \) matrix \( M \), where:
\[
M_{jk} = 
\begin{cases} 
\frac{1}{\text{deg}(k)} & \text{if } (j, k) \in E, \\
0 & \text{otherwise}.
\end{cases}
\]
The initial probability distribution \( p \) over the vertices updates to \( p' = M p \) after one step.

For quantum walks, maintaining unitarity requires a \textit{coin operator} \( C \) to determine the direction of the next step. A common choice for the coin operator is the Grover diffusion operator, defined as:
\[
C := \sum_{j \in V}\ket{j}\bra{j} \otimes (2\ket{\partial_j}\bra{\partial_j} - I),
\]
where:
\[
\ket{\partial_j} := \frac{1}{\sqrt{\deg(j)}} \sum_{k:(j,k) \in E}\ket{k},
\]
denotes the superposition of the neighboring vertices of \( \ket{j} \), and \( I \) is the identity matrix.

One step of the discrete-time quantum walk is described by the unitary operator \( SC \), where \( S \) is the swap operator:
\[
S = \sum_{(j,k) \in E}\ket{j,k}\bra{k,j}.
\]

\subsection*{Comparison of Models}
The continuous-time model is simpler to define and analyze, often leading to exponential speedups under specific conditions, such as graphs with small maximum degrees. However, discrete-time quantum walks are easier to implement using quantum circuits, making them more practical in many applications. For example, while continuous-time models may struggle with certain problems like \textit{element distinctness}, discrete-time models handle them more effectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Group Actions}

Group actions provide a framework for understanding how groups interact with sets, formalizing the concept of applying transformations systematically. They capture the symmetries and structure-preserving transformations of objects, making them fundamental in mathematics and its applications. Group actions describe transformations through a set of rules that ensure consistency and compatibility with the underlying group operations. This concept is pivotal in cryptography, where the symmetries and operations of groups underpin many secure systems.

In cryptography, group actions are critical to protocols like Elliptic Curve Cryptography (ECC), which relies on the difficulty of reversing group-based operations to ensure security. Isogeny-based cryptography, a post-quantum cryptographic candidate, uses group actions on elliptic curves to create complex mathematical problems resistant to quantum attacks. Similarly, lattice-based and code-based cryptography use group actions to study transformations in structures that form the basis for secure communication systems. Non-abelian group actions are being explored for their potential to create quantum-resistant algorithms.

In quantum computing, group actions are central to quantum walks, a quantum equivalent of classical random walks. Quantum walks leverage group actions to describe the evolution of quantum states and exploit the symmetries of these states for tasks like search, optimization, and cryptographic protocol design. This makes them valuable in constructing secure quantum algorithms and protocols, particularly in quantum key distribution and graph-based cryptography. Overall, group actions bridge abstract mathematical theory with practical applications in classical and quantum cryptography.

\section*{Definition of Group Action}

Group actions form a bridge between group theory and other mathematical structures, offering a systematic way to study symmetry, transformations, and invariants. Let us delve deeper into their properties, classifications, and applications.

\subsection*{Formal Definition}

A \textbf{group action} of a group \( G \) on a set \( X \) is a map \( \cdot : G \times X \to X \) that satisfies:

\begin{enumerate}
    \item \textbf{Identity Property}:
    \[
    e \cdot x = x \quad \text{for all } x \in X,
    \]
    where \( e \) is the identity element of \( G \).

    \item \textbf{Compatibility (Associativity)}:
    \[
    (gh) \cdot x = g \cdot (h \cdot x) \quad \text{for all } g, h \in G, \, x \in X.
    \]
\end{enumerate}

Alternatively, the group action can be viewed as a homomorphism \( \phi : G \to \text{Sym}(X) \), where \( \text{Sym}(X) \) is the group of all permutations of \( X \).

\subsection*{Types of Group Actions}

\begin{enumerate}
    \item \textbf{Faithful Action}: The action is faithful if \( g \cdot x = x \) for all \( x \in X \) implies \( g = e \). Equivalently, the homomorphism \( \phi \) is injective.

    \item \textbf{Transitive Action}: The action is transitive if, for any \( x, y \in X \), there exists \( g \in G \) such that \( g \cdot x = y \). In this case, \( X \) consists of a single orbit.

    \item \textbf{Free Action}: The action is free if \( g \cdot x = x \) implies \( g = e \) for all \( x \in X \).

    \item \textbf{Regular Action}: The action is both transitive and free, meaning there is exactly one \( g \in G \) for each pair \( (x, y) \) such that \( g \cdot x = y \).

    \item \textbf{Effective Action}: The action is effective if the only group element acting as the identity on \( X \) is \( e \).
\end{enumerate}

\subsection*{Key Concepts in Group Actions}

\begin{enumerate}
    \item \textbf{Orbits}:
    For \( x \in X \), the \textbf{orbit} of \( x \) is:
    \[
    \text{Orb}(x) = \{g \cdot x \mid g \in G\}.
    \]
    Orbits partition the set \( X \), and each orbit is a subset where the action appears ``connected.''

    \item \textbf{Stabilizer Subgroup}:
    The \textbf{stabilizer} of \( x \in X \) is:
    \[
    \text{Stab}_G(x) = \{g \in G \mid g \cdot x = x\}.
    \]
    It is a subgroup of \( G \) and describes the symmetries that leave \( x \) unchanged.

    \item \textbf{Orbit-Stabilizer Theorem}:
    This theorem links the size of an orbit and its stabilizer:
    \[
    |G| = |\text{Orb}(x)| \cdot |\text{Stab}_G(x)|.
    \]

    \item \textbf{Fixed Points}:
    A point \( x \in X \) is a \textbf{fixed point} if \( g \cdot x = x \) for all \( g \in G \). The set of fixed points is:
    \[
    \text{Fix}(G) = \{x \in X \mid g \cdot x = x, \, \forall g \in G\}.
    \]

    \item \textbf{Invariant Subsets}:
    A subset \( Y \subseteq X \) is \textbf{invariant} under the action if \( g \cdot y \in Y \) for all \( g \in G \) and \( y \in Y \).
\end{enumerate}

\subsection*{Equivalence Relations Induced by Group Actions}

The orbits of a group action define an equivalence relation on \( X \), where \( x \sim y \) if there exists \( g \in G \) such that \( g \cdot x = y \).

\begin{itemize}
    \item \textbf{Equivalence Classes}: The orbits of the action.
    \item \textbf{Quotient Set}: The set of orbits, denoted \( X/G \).
\end{itemize}

\subsection*{Quantum walks from Group Actions}
The spectral decomposition of the adjacency matrix of a Cayley graph generated by a general group action $G$ provides insights into the structure and properties of the graph. This decomposition leverages the symmetries of the group $G$ and representation theory to analyze the eigenvalues and eigenvectors of the adjacency matrix.

Let $G$ be a finite group, and let $X$ be a set on which $G$ acts via a group action $G \times X \to X$. A Cayley graph can be constructed based on this action, where
the vertices are the elements of the set $X$, and For each $g \in G$ and $x \in X$, there is an edge between $x$ and $g *	x$, where $g * x$ is the action of $g$ on $x$.

If the generating set $S \subset G$ is symmetric (i.e., $s \in S \implies s^{-1} \in S$), then the Cayley graph is undirected. Otherwise, it may be directed.

The adjacency matrix $A$ of the Cayley graph is a matrix that encodes the edges of the graph:

\[
A_{x,y} =
\begin{cases}
1, & \text{if there exists } g \in G \text{ such that } y = g * x, \\
0, & \text{otherwise}.
\end{cases}
\]

The adjacency matrix is symmetric if the group action preserves symmetry, which happens if $G$ is acting via an involution, i.e., if for every generator $g \in G$, its inverse is also a generator. It also inherits the symmetries of the group action. That is, the group $G$ acts on the vertices of the graph, and the adjacency matrix commutes with the action of the group. This means that the adjacency matrix $A$ is highly structured, and its eigenvalues can be computed using the representation theory of the group $G$.

The eigenvalues of the adjacency matrix correspond to the eigenvalues of these blocks $\rho(A)$, and the multiplicities of the eigenvalues are related to the dimensions of the corresponding irreducible representations.

The spectral decomposition of the adjacency matrix $A$ can be written as:

\[
A = \sum_{i} \lambda_{i} v_{i} v_{i}^{\top},
\]

where:

- $\lambda_{i}$ are the eigenvalues,
- $v_{i}$ are the corresponding eigenvectors (which lie in the spaces corresponding to the irreducible representations),
- $v_{i} v_{i}^{\top}$ is the outer product of the eigenvector $v_{i}$ with itself.

The eigenvectors $v_{i}$ are related to the characters of the group $G$. Specifically, the characters of irreducible representations of $G$ help determine the eigenvalues of $A$. If $\chi_{\rho}$ denotes the character of the irreducible representation $\rho$, then the eigenvalues are given by:

\[
\lambda_{\rho} = \frac{1}{|G|} \sum_{g \in G} \chi_{\rho}(g) A(g),
\]

where $A(g)$ is the action of $g$ as represented in the adjacency matrix.

@@

\section*{Quantum Hartley Transform (QHT)}

The \textbf{Quantum Hartley Transform (QHT)} is a linear unitary transform that operates on quantum states. It transforms the basis states \( |x\rangle \) as follows:
\[
|x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \text{cas}\left(\frac{2\pi x k}{N}\right) |k\rangle
\]
where:
\begin{itemize}
    \item \( x \) and \( k \) are integers in \( \{0, 1, \dots, N-1\} \),
    \item \( \text{cas}(x) = \cos(x) + \sin(x) \),
    \item \( N \) is the dimension of the transform, typically \( 2^n \) for \( n \)-qubit systems.
\end{itemize}

For a quantum state \( |\psi\rangle \) in an \( N \)-dimensional Hilbert space, represented as:
\[
|\psi\rangle = \sum_{x=0}^{N-1} \psi_x |x\rangle,
\]
the QHT transforms the state into:
\[
|\psi'\rangle = \text{QHT} |\psi\rangle = \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left( \sum_{x=0}^{N-1} \psi_x \, \text{cas}\left(\frac{2\pi x k}{N}\right) \right) |k\rangle.
\]

\subsection*{Properties of the QHT}
\begin{enumerate}
    \item \textbf{Unitary Transformation}: The QHT matrix \( U_{\text{QHT}} \) is unitary:
    \[
    U_{\text{QHT}} U_{\text{QHT}}^\dagger = I,
    \]
    preserving quantum state normalization.
    \item \textbf{Symmetry}: The QHT is symmetric because \( \text{cas}(x) = \text{cas}(-x) \).
    \item \textbf{Efficient Implementation}: Like the Quantum Fourier Transform (QFT), the QHT can be implemented with \( O(\log^2 N) \) gates for \( N = 2^n \).
\end{enumerate}

\subsection*{Comparison with the Quantum Fourier Transform (QFT)}
The QFT and QHT differ in their transformation kernels:
\begin{itemize}
    \item \textbf{QFT}:
    \[
    |x\rangle \xrightarrow{\text{QFT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} e^{2\pi i x k / N} |k\rangle.
    \]
    \item \textbf{QHT}:
    \[
    |x\rangle \xrightarrow{\text{QHT}} \frac{1}{\sqrt{N}} \sum_{k=0}^{N-1} \left[\cos\left(\frac{2\pi x k}{N}\right) + \sin\left(\frac{2\pi x k}{N}\right)\right] |k\rangle.
    \]
\end{itemize}

\subsection*{Applications of the QHT}
\begin{itemize}
    \item \textbf{Signal Processing}: Analysis of real-valued signals in quantum systems.
    \item \textbf{Quantum Algorithms}: Used in problems where real and symmetric basis representations simplify computations.
    \item \textbf{Data Compression}: Efficient representation of signals with high symmetry.
\end{itemize}
